---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pivotea

<!-- badges: start -->
<!-- badges: end -->

The goal of screenshot is to take a screenshot easily and locate image position on a display with R.


## Installation

You can install the development version of pivotea from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
remotes::install_github("matutosi/screenshot")
```

On Win OS, need to install screenshot.exe by `install_screenshot()`.
This exe file is compiled from codes shown below.

https://superuser.com/questions/75614/take-a-screen-shot-from-command-line-in-windows#answer-1751844

```{r, eval = FALSE}
dir <- fs::path_package("screenshot")
  # if you want to install another directory
  #   dir <- "SET_YOUR DIRECTORY"
install_screenshot(dir)
```

<!-- 
You can also install from CRAN:

```{r, eval = FALSE}
install.packages("screenshot")
```
-->

## Example

You can use `screenshot()` to take a screenshot easily.

```{r example, eval = FALSE}
library(screenshot)
library(dplyr)
library(imager)
sc <- screenshot()
sc_image <- imager::load.image(sc)
plot(sc_image)
```


To locate image from a screenshot, use `locate_image()`.

```{r example, eval = FALSE}

```


## Citation

Toshikazu Matsumura (2023) Screenshot and locate image Easily. https://github.com/matutosi/screenshot/.
